### 2023-09-20 3.Design/crossbar.tex
Finishing at the library

The crossbar circuit theory has already been explained in the \cref{sec:crossbar}. This section describes how the crossbar circuit is actually implemented. The final circuit is the one in \cref{circt:xbar}. The circuit depends on three parameters :
\begin{itemize}
  \item $n_i$ : The number of input for our crossbar array (not including bias for a more general circuit).
  \item $n_o$ : The number of parallel output for our crossbar array.
  \item $n_s$ : The serial size of our crossbar system.
\end{itemize}

@@

The crossbar system, and in a more general manner, the entire system will require an external controller to control the enable flags that are required in the system. Adding such a system will increase the power consumption of the overall system. However, due to the slow (precision of about $1\mu s$) nature of those signals, the controller will be very low power, and won't change the overall power consumption of the final system.%TODO maybe move to final circuit

>>>>

The crossbar circuit theory has already been explained in the \cref{sec:crossbar}. This section describes how the crossbar circuit is actually implemented. The final circuit is the one in \cref{circt:xbar}. The circuit depends on three parameters :

\begin{itemize}
  \item $n_i$ : The number of input for our crossbar array (not including bias for a more general circuit).
  \item $n_o$ : The number of parallel output for our crossbar array.
  \item $n_s$ : The serial size of our crossbar system.
\end{itemize}

@@
